---
title: "INFO 3010 - Assignment 2"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, Feb 3, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Fill in the code chunks and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1 (5pts): Download the file 'Adults_Cleaned.csv' from canvas. Read the file into a dataframe.
```{r}
setwd('/Users/anime/Documents/Data science')
adults<- read.csv('Adults_Cleaned.csv')
```

### Q2: (3pts) Write code to show first 5 lines of the dataset.
```{r}

head(adults,5)
```

### Q3: (3pts) How many samples are in the dataset? 
```{r}

nrow(adults)
```

### Q4: (4pts) Check the data types of each column.
```{r}
str(adults)


```

### Q5: (5pts) How many kinds of occupations are in the dataset?
```{r}
uni<-unique(adults[,7])
length(uni)
```

### Q6: (5pts) A statistical summary of the dataset.
```{r}
summary(adults)
```

### Q7: (5pts) How many people have capital gain more than 0?
```{r}
nrow(adults[adults$capital.gain >"0",]) 

```

### Q8: (5pts) How many people work more than 40hrs a week?
```{r}
nrow(adults[adults$hours.per.week > 40,])

```

### Q9: (5pts) Number of people whose native country is Mexico and work more than 40hrs a week.
```{r}
nrow(adults[(adults$hours.per.week > 40) & (adults$native.country == "Mexico"),])
```

### Q10: (5pt) For people who have got bachelor education or higher, what the is percentage to have income more than 50K?
```{r}
more50work40<-nrow(adults[(adults$education.num >= 13 )&(adults$label=='>50K'),])
educationOnly<-nrow(adults[(adults$education.num >= 13),])
percent <- more50work40/educationOnly*100
print(percent)

```

### Q11: (5pts) What is the average woking hours per week for people who are husband?
```{r}

HusbansMean<-mean(adults[adults["relationship"] == "Husband","hours.per.week"])
print(HusbansMean)

```

