---
title: "INFO 3010 - Assignment 4"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, Feb 17, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1. (5pts) Import the json file to R
```{r}
library(jsonlite)
library(XML)
library(RCurl)
setwd('/Users/anime/Documents/Data science')
fileURL = 'https://unt.instructure.com/courses/24073/assignments/490410?module_item_id=1521324'

xData<- stream_in(file("snowstorm_sample.json"))

```

### Q2. (5pts) How many records are there in the json file?
```{r}

nrow(xData)
```

### Q3. (5pts) Extract information of 'created_at', 'id_str', 'id' of 'user', 'name' of 'user', 'full_name' of 'place', 'place_type' of 'place' from the json file and generate 6 vectors named as 'create_at', 'tweet_id', 'user_id','user_name','place_name','place_type'.
```{r}
created_at = xData$created_at
tweet_id = xData$id_str
user_id = xData$user$id
user_name = xData$user$name
place_name = xData$place$full_name
place_type = xData$place$place_type
```

### Q4. (5pts) Create a dataframe with the 6 vectors.
```{r}
dataframe <-data.frame(created_at,tweet_id, user_id,user_name, place_name,place_type)
dataframe
```

### Q5. (5pts) Check the first 10 lines of the data frame.
```{r}
head(dataframe,10)
```

### Q6. (5pts) How many tweets are labeled with a place_type as 'city'?
```{r}
nrow(dataframe[dataframe$place_type == 'city',])
```

### Q7. (10pts) How many unique users are there in the dataset?
```{r}

users<-nrow(dataframe[unique(dataframe$user_name),])
users
```

### Q8. (10pts) How many tweets have place_name as 'Washington, DC'
```{r}
place<- nrow(dataframe[dataframe$place_name == 'Washington, DC',])
places
```

