---
title: "INFO 3010 - Assignment 8"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Spring 2020 by Lingzi Hong
## Due: Monday, April 13, 2020
### Instructions
1. This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button, all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.
2. Please download the snowstorm.json from canvas. Fill in the code chunks for following question and submit this R markdown file to the assignment on Canvas. Make sure when you save that you have run all cells, so the outputs displace between the cells.
3. make sure to replace the directoryID in the filename with your student ID. 


### Q1. (5pts)  Create a function that can convert fahrenheit to celsius. The formula is (F-32)*5/9 = C. Fill in the function body. There is a test case to convert fahrenheit 86 to celsius. 
```{r}
fahrenheit_to_celcius <- function(tempf){
  tempc <- (tempf-32)*5/9
  return(tempc)
}
fahrenheit_to_celcius(86)
```

### Q2. (5pts) Read the file '2016.csv' to a dataframe. Check the first 5 lines of the data. 
```{r}
library("ggplot2")
setwd('/Users/anime/Documents/Data science' )

dataf <- read.csv('2016.csv')

head(dataf,5)
```

### Q3. (5pts) Use the dataframe in Q3. Compute the average Hapiness_Score for countries in North America. 
```{r}
naHappy <- dataf[(dataf$Region == 'North America'),]
naHappy
mean(naHappy$Happiness_Score)
```

### Q4. (5pts) Use the dataframe in Q3. Write code to compute the difference in Generosity between United States and Mexico.
```{r}
UnitedStates <- naHappy[(naHappy$Country == 'United States'),]
Mexico <- dataf[(dataf$Country == 'Mexico'),]
difference = (UnitedStates$Generosity)-(Mexico$Generosity)

difference
```

### Q5. (5pts) Use the dataframe in Q3. Plot the dataframe columns Happiness_Rank and Happiness_Score as a line graph

```{r}
happinessLine <- ggplot(data = naHappy ,aes(x = Happiness_Score, y=Happiness_Rank))
happinessLine+geom_line()
```

### Q6. (5pts) Use the dataframe in Q3. Plot the scatter plot matrix for the four variables: Family, Life_Expectancy,Freedom, Generosity
```{r}
scatterPlot <- subset(naHappy,select = c(Family,Life_Expectancy,Freedom,Generosity))
pairs(scatterPlot)
```

### Q7. (5pts) Get a subset of data with countries from Region of "Western Europe" and "North America" and "Eastern Asia".
```{r}
subsetdataf <- dataf[(dataf$Region == "Western Europe")| (dataf$Region == "North America") | (dataf$Region == "Eastern A"),]
head(subsetdataf,20)
```
### Q8. (5pts) Use the subset data in Q8. Draw a scatter plot with Government_Corruption in the x-axis, Freedom in the y-axis, and the points are colored by region. 
```{r}
scatter <- ggplot(subsetdataf)+geom_point(mapping = aes(x = Government_Corruption,y= Freedom,color = Region))
scatter
```

### Q9. (5pts) Build a linear regression model: predict Happiness_Score with variables GDP_per_Capita, Family, Life_Expectancy and Freedom. 
```{r}
Happinessmodel <- lm(Happiness_Score~GDP_per_Capita+ Family+ Life_Expectancy+Freedom , data =train)
```
### Q10. (5pts) Get a summary of the model. Answer the following questions out of the code chunk: what is the adjusted R-squared? What is the coefficient of GDP_per_Capita?

A: Based on what i see the adjusted R-Squared is 0.7461 and the coefficients of GDP_per_Capita is 1.4891 for Estimated Standard deviation, error is 0.6435, t value is 2.315 and Pr(>|t|) is 0.0538.
```{r}
summary(Happinessmodel)
```
